DNSKEY Management

### 2012-12-05 paper/paper.tex
initials instead of footnotes for paragraph authors.

\title{DNSKEY Management}
\author{Julien Perrochet \and Tobias Schlatter}
\date{December 12, 2012}

@@

\newcommand{\wbjp}{\protect\footnote{Written by Julien Perrochet}}
\newcommand{\wbts}{\protect\footnote{Written by Tobias Schlatter}}

@@

In the DNS world, the \emph{friend} we trust is the so-called root authority -- the root domain in DNSSEC -- of whom we know the public key in advance.

@@

\paragraph{Key Rollover} RFC4641 \cite{RFC4641} suggests that the DNSKEY
records for a zone should be changed somewhere between once every week
up to once every month. While the detailed rollover procedure is
irrelevant here, it is important to know, that the parent zone has to
update its DS record.

@@

\subsection{Penetration in Production}
In figure~\ref{fig:dnssec-growth} you can see the development of
deployed, production DNSSEC zones. The data comes from SecSpider
\cite{secspider} which crawls as many DNSSEC zones as possible,
verifies whether it is properly signed and then applies a heuristics to
determine whether it is actually a production zone. The goal is to
rule out zones which are created for testing such as
\url{bogussig.bogussig.test.jelte.nlnet.labs.nl}.

@@

The Internet Software Consortium (ISC) still runs an inline TAR
\cite{iscDlv}, using the DNSSEC Lookaside Validation standard
\cite{RFC5074}. When a resolver needs to check the key of a zone
\verb|<X>| with this TAR, it makes a DNS request of type DLV to 
\url{<X>.dlv.isc.org}. If it succeeds, the DLV record contains the
signature for the (hopefully matching) DNSKEY. The ISC inline TAR
requires manual addition of keys to the repository.

@@

\subsubsection{Single administrative domain}
Basically, once an organization has its main domain signed, it is relatively easy for any sub-entity within said organization to get a sub-domain signed, and to coordinate any operations relative to DNSSEC like key rollover: staying with our EPFL example, it can suffice to contact the IT-department and discuss about the procedure with them\footnote{EPFL does not actually use DNSSEC, but we use the school as an example for the sake of simplicity.}. The bottom line is that it is relatively easy to handle the additional work and information updates required by DNSSEC as long as every concerned party lies within the same organization.
\subsubsection{Multiple administrative domain}
DNSSEC's true challenges arise when we begin to consider several administrative entities (the three R's, mainly). As stated earlier, once the \verb|epfl.ch| zone is signed it is easy for the school to sign \verb|www.epfl.ch|. However, if the domain to be signed was \verb|epfl.ch| or \verb|epfl.ae|, the school would have to deal with the entity or entities managing the TLD's (\verb|ch.| managed by Switch or \verb|ae.|\footnote{epfl.ae has been registered at 'Instra Corporation Pty Ltd', a registrar for the ae.}, respectively), which will have they own terms and conditions, which might very well be different among different registrars and TLD's.

@@

As suggested by some RFC\footnote{RFC 4641}, key updates should  happen at least every few months. Hence, it is crucial that a streamlined and reactive process is available for child-zones to notify their parent-zone when required. In the three R's setup, this means that the registry (or the registrars) must provide means for registrants to easily inform them of any changes regarding their DNSSEC keys.
%TODO process figure with Registrant -> Registrar -> Registry ?

>>>>

\title{DNSKEY Management}
\author{Julien Perrochet [JP] \and Tobias Schlatter [TS]}
\date{December 12, 2012}

@@

\newcommand{\wbjp}{\textsuperscript{JP}}
\newcommand{\wbts}{\textsuperscript{TS}}

@@

In the DNS world, the \emph{friend} we trust is the so-called root authority -- the root domain -- of whom we know the public key in advance.

@@

\paragraph{Key Rollover} RFC4641 \cite{RFC4641} suggests that the DNSKEY
records for a zone should be changed somewhere between once every week
up to once every month. While the detailed rollover procedure is
irrelevant here, it is important to know that the parent zone has to
update its DS record regularly.

@@

\subsection{Penetration in Production}
In figure~\ref{fig:dnssec-growth} you can see the development of
deployed, production DNSSEC zones. The data comes from SecSpider
\cite{secspider} which crawls as many DNSSEC zones as possible,
verifies whether they are properly signed and then applies a heuristic to
determine whether it is actually a production zone. The goal is to
rule out zones which are created for testing such as
\url{bogussig.bogussig.test.jelte.nlnet.labs.nl}.

@@

The Internet Software Consortium (ISC) still runs an inline TAR
\cite{iscDlv}, using the DNSSEC Lookaside Validation standard~\cite{RFC5074}. When a resolver needs to check the key of a zone
\verb|<X>| with this TAR, it makes a DNS request of type DLV to 
\url{<X>.dlv.isc.org}. If it succeeds, the DLV record contains the
signature for the (hopefully matching) DNSKEY. The ISC inline TAR
requires manual addition of keys to the repository.

@@

Enabling DNSSEC for a zone not being a \emph{do once and forget} operation, but instead requires additional coordination among the three R's, let us see what the managerial consequences arise, depending on if we cross or stay within certain administrative boundaries.

\subsubsection{Single administrative domain}
Basically, once an organization has its main domain signed, it is relatively easy for any sub-entity within said organization to get a sub-domain signed, and to coordinate any operations relative to DNSSEC like key rollover: staying with our EPFL example, it can suffice to contact the IT-department and discuss about the procedure with them\footnote{EPFL does not actually use DNSSEC, but we use the school as an example for the sake of simplicity.}. The bottom line is that it is relatively easy to handle the additional work and information updates required by DNSSEC as long as every concerned party lies within the same organization.

\subsubsection{Multiple administrative domain}
DNSSEC's true challenges arise when we begin to consider several administrative entities (the three R's, mainly). As stated earlier, once the \verb|epfl.ch| zone is signed it is easy for the school to sign \verb|www.epfl.ch|. However, if the domain to be signed was \verb|epfl.ch| or \verb|epfl.ae|, the school would have to deal with the entity or entities managing the TLD's (\verb|ch.| managed by Switch or \verb|ae.|\footnote{epfl.ae has been registered at 'Instra Corporation Pty Ltd', a registrar for the ae.}, respectively), which will have they own terms and conditions, which might very well be different among different registrars and TLD's.

@@

As suggested by some RFC\cite{RFC4641} key updates should  happen at least every few months. Hence, it is crucial that a streamlined and reactive process is available for child-zones to notify their parent-zone when required. In the three R's setup, this means that the registry (or the registrars) must provide means for registrants to easily inform them of any changes regarding their DNSSEC keys.
%TODO process figure with Registrant -> Registrar -> Registry ?
